D.I.A.G.R.A.M.: Digital Image Analysis for Graph Recognition And Modeling

### 2025-07-09 doc/article/article.tex
Fix

\subsubsection{Text Association}
It can be assumed that every piece of text is linked to one and only one element or relation. So, every bounding box containing text is linked to the nearest element - it being either a relation or a node. The associations that require too long a distance are eliminated further in the algorithm, and the associated text is discarded.\\

@@

\subsubsection{Arrow-Text Association}
After a text box is assigned to an arrow, some computation is needed to fully understand how the text is associated to the arrow itself. The arrow is approximated by a line adjoining its head and its tail.
The distance between the line and the text's bounding box is computed and compared with a threshold - if it's over it, the association is discarded.
Otherwise, the line approximation is then split into three different sections - whose sizes are heuristically determined, such that the relation's central section is bigger than the other two. The distance between the text bounding box and each of the three sections boxes is computed - then, the section with the lowest distance value is then assigned to the text under consideration.
We must notice that for self-arrow we can not compute simple distance between the line and the text's bounding box, given that the approximated arrow line is not accurate. Thus, we approximate the arrow using two segments like a triangle.
The third point is the middle of the opposite edge. \\

>>>>

\subsubsection{Text Association}
It can be assumed that every piece of text is linked to one and only one element or relation. Thus, every bounding box containing text is linked to the nearest element - it being either a relation or a node - based on their distance. The associations that require too long a distance are eliminated further in the algorithm, and the associated text is discarded.
We must notice that for self-arrow we can not compute simple distance between the line and the text's bounding box, given that the approximated arrow line is not accurate. Thus, we approximate the arrow using two segments like a triangle.
The third point is the middle of the opposite edge. \\

@@

\subsubsection{Arrow-Text Association}
After a text box is assigned to an arrow, some computation is needed to fully understand how the text is associated to the arrow itself. The arrow is approximated by a line adjoining its head and its tail.
The distance between the line and the text's bounding box is computed and compared with a threshold - if it's over it, the association is discarded.
Otherwise, the line approximation is then split into three different sections - whose sizes are heuristically determined, such that the relation's central section is bigger than the other two. The distance between the text bounding box and each of the three sections boxes is computed - then, the section with the lowest distance value is then assigned to the text under consideration. \\
